\section{Structure for the research plan}\label{chapter:appendices}
	
	A research plan can be reported according to the next structure. The order of the items is 
	important.
	
	\begin{refsection}
		\subsection*{Introduction }
		The topic is introduced on general level. The context of the research is described and the 
		research  problem  is  explained  and  justified.  The  problem  is  situated  in  its  larger 
		environment. Note references when needed. The researcher may reason the topic also by 
		describing his or her personal motivation.
		\subsection*{Research problem and research methods }
		The problem under study is explained as explicitly as possible. The research problem 
		can be divided into sub problems or presented as hypotheses. The research methods and 
		analysis are described. 
		\subsection*{Limitations}
		The planned limitations and known shortcomings are reported. The reasons for them – if 
		known – are explained from the viewpoint of the current research.
		
		\subsection*{Preliminary earlier research}
		The prior literature is presented briefly with full sentences. All required references are 
		included. Its relevance in the current research is described and limitations recognised in 
		prior research are identified if possible. 
		List of main prior literature in relation to the background theory 
		Main background references are listed in the required format (APA).
		
		\subsection*{Lähteet}
		%\nocite{*}
		%\bibliographystyle{apacite}
		%\bibliography{refs}
		% \printbibliography[heading=none]
	\end{refsection}
	
	\subsection*{Timetable }
	A plan to describe the planned research related to calendar time. It is recommended that 
	the  plan  is  discussed  with  supervisor  to  ensure  enough  milestones  for  checking 
	thoroughly the status of the thesis.
	
	\subsection*{Preliminary structure of contents }
	\begin{enumerate}
		\item Introduction
		\item Glossary
		\item Prior research
		\begin{enumerate} 
			\item First
			\item Second
			\subitem Subsecond
		\end{enumerate}		
		\item Sources
	\end{enumerate}
	